### 2015-06-30 Projects/DelCo_2014/Report/Hose_Stream_Report/Report/DelCo_Hose_Tests_2014.tex
DelCo_2014: Added content to hose report, including new pictures and drawings

\section{Instrumentation}
\label{sec:Instrumentation}
Schematic plan overviews of the instrumentation in the East and West Structures are shown in Fig.~\ref{fig:east_instrumentation} and Fig.~\ref{fig:west_instrumentation}, respectively. There is a discussion of uncertainties for each measurement below in Section~\ref{sec:Uncertainty}. Gas velocity was measured at various doorways using differential pressure transducers connected to bi-directional velocity probes~\cite{McCaffrey:Combustion_and_Flame}. Each set of BDPs contained 8 probes located at distances of 0.08 m, 0.34 m, 0.61 m, 0.88 m, 1.15 m, 1.42 m, 1.68 m, and 1.95 m below the soffit of the corresponding doorway. Fig.~\ref{fig:BDPs} shows a picture of two sets of BDPs, A5 and A6, located at each double door on the first floor of the West Structure. A single thermocouple was attached to each bi-directional probe. The thermocouples used with the bi-directional probes are exposed-bead, Chromel-Alumel (type K) with a 1.0 mm (0.04 in) diameter. Starting with the exposed bead, the thermocouple wire was sheathed in a 3.2 mm (0.13 in) diameter Inconel shield, 0.76 m (2.5 ft) in length.

%\begin{figure}[!ht]
%\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../../Drawings/PDFs/With_Instrumentation/East_Test_Structure_Devices_Hose_Test}
%\caption[Location of Instrumentation in East Structure]{Location of Instrumentation in East Structure}
%\label{fig:east_instrumentation}
%\end{figure}

@@

%\begin{figure}[!ht]
%\includegraphics[width=6in]{../../Figures/flow_meter}
%\caption[Picture of Flowrate Meter]{Pressure and flow meter combination used to measure water flowrate}
%\label{fig:flow_meter}
%\end{figure}

@@

Test 33 varied from Tests 29 and 30 in multiple ways. First, for Test 33, the monitor was located inside Room C and aimed at the ceiling of Room B, as pictured in Fig.~\ref{fig:Test_33_34_setup}. Additionally, Test 33 began by flowing water in a straight stream pattern for 30 seconds, then in a narrow fog stream for 30 seconds, and finally in a wide fog stream for 30 seconds. Then, the south side door was opened, and each stream was applied for 30 seconds again.

@@

Tests 31 and 32 followed an identical procedure that involved flowing water from the north side double doors using a handline with a combination nozzle. A straight stream pattern was used during Test 31, and a narrow fog stream pattern was used during Test 32. Each test began by flowing water with the nozzle aimed at the ceiling of Room C (marked in Fig.~\ref{fig:Test_31_32_setup}) in the fixed position. After 30 seconds had elapsed, the nozzle was rotated in the clockwise direction and then returned to the fixed position of 30 seconds. Next, the nozzle was rotated in the counter-clockwise direction for 30 seconds, and then returned to the fixed position for 30 seconds. While the nozzle was in the fixed position, the south side door was opened and the application patterns were repeated. After the patterns were applied with the south side door opened, the door was closed, the handline was aimed at Door BC, and each pattern was applied again for 30 seconds while the south side door was opened and closed. This entire procedure was repeated an additional time.

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_31_32}
\caption[East Structure layout for Tests 31 and 32]{East Structure layout for Tests 31 and 32.}
\label{fig:Test_31_32_setup}
\end{figure}
\FloatBarrier

Test 34 varied from Tests 31 and 32 in multiple ways. First, for Test 34, the handline was located inside Room C and aimed at the ceiling of Room B, as pictured in Fig.~\ref{fig:Test_33_34_setup}. Additionally, Test 34 began by flowing water in a straight stream at the ceiling in Room B for 30 seconds in a fixed position and then for 30 seconds in a clockwise application pattern. Then, the handline was aimed at Door AB, and again water was applied for 30 seconds in a fixed position and for 30 seconds in a clockwise pattern. These steps were repeated for narrow fog and wide fog streams. Additionally, the procedure was repeated for the three types of streams, except a counter clockwise pattern was applied.

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_34}
\caption[East Structure layout for Tests 31 and 32]{East Structure layout for Tests 31 and 32.}
\label{fig:Test_34_setup}
\end{figure}
\FloatBarrier

>>>>

\section{Instrumentation}
\label{sec:Instrumentation}
Schematic plan overviews of the instrumentation in the East and West Structures are provided in Fig.~\ref{fig:east_instrumentation} and Fig.~\ref{fig:west_instrumentation}. There is a discussion of uncertainties for each measurement below in Section~\ref{sec:Uncertainty}. Gas velocity was measured at various doorways using differential pressure transducers connected to bi-directional velocity probes~\cite{McCaffrey:Combustion_and_Flame}. Each set of BDPs contained 8 probes located at distances of 0.08 m, 0.34 m, 0.61 m, 0.88 m, 1.15 m, 1.42 m, 1.68 m, and 1.95 m below the soffit of the corresponding doorway. Fig.~\ref{fig:BDPs} shows a picture of two sets of BDPs, A5 and A6, located at each double door on the first floor of the West Structure. A single thermocouple was attached to each bi-directional probe. The thermocouples that are used with the bi-directional probes are exposed-bead, Chromel-Alumel (type K) with a 1.0 mm (0.04 in) diameter. Starting with the exposed bead, the thermocouple wire was sheathed in a 3.2 mm (0.13 in) diameter Inconel shield, 0.76 m (2.5 ft) in length.

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../Pictures/flow_meter}
\caption[Picture of Flowrate Meter]{Pressure and flow meter combination used to measure water flowrate}
\label{fig:flow_meter}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../Pictures/East_monitor_C_BC.pdf}
\caption[Straight Stream and Narrow Fog Stream during Tests 29 and 30]{Straight stream (left) and narrow fog stream (right) aimed at ceiling of Room C (top) and Door BC (bottom) during Tests 29 and 30}
\label{fig:test_29_30_pic}
\end{figure}
\FloatBarrier

Test 34 varied from Tests 29 and 30 in multiple ways. First, for Test 33, the monitor was located inside Room C and aimed at the ceiling of Room B, as pictured in Fig.~\ref{fig:Test_33_setup}. Additionally, Test 33 began by flowing water in a straight stream pattern for 30 seconds, then in a narrow fog stream for 30 seconds, and finally in a wide fog stream for 30 seconds. Then, the south side door was opened, and each stream was applied for 30 seconds again.

@@

Tests 31 and 32 followed an identical procedure that involved flowing water from the north side double doors using a handline with a combination nozzle. A straight stream pattern was used during Test 31, and a narrow fog stream pattern was used during Test 32. Each test began by flowing water with the nozzle aimed at the ceiling of Room C (marked in Fig.~\ref{fig:test_29-32_setup}) in the fixed position. After 30 seconds had elapsed, the nozzle was rotated in the clockwise direction and then returned to the fixed position of 30 seconds. Next, the nozzle was rotated in the counter-clockwise direction for 30 seconds, and then returned to the fixed position for 30 seconds. While the nozzle was in the fixed position, the south side door was opened and the application patterns were repeated. After the patterns were applied with the south side door opened, the door was closed, the handline was aimed at Door BC, and each pattern was applied again for 30 seconds while the south side door was opened and closed. This entire procedure was repeated an additional time.

\begin{figure}[!ht]
\includegraphics[width=6in]{../Pictures/East_handline_C_BC.pdf}
\caption[Straight Stream and Narrow Fog Stream during Tests 31 and 32]{Straight stream (left) and narrow fog stream (right) aimed at ceiling of Room C (top) and Door BC (bottom) during Tests 31 and 32}
\label{fig:test_31_32_pic}
\end{figure}
\FloatBarrier

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_29-32}
\caption[East Structure layout for Tests 29-32]{East Structure layout for Tests 29-32}
\label{fig:test_29-32_setup}
\end{figure}
\FloatBarrier

Test 34 varied from Tests 31 and 32 in multiple ways. First, for Test 34, the handline was located inside Room C and aimed at the ceiling of Room B, as pictured in Fig.~\ref{fig:test_33_34_setup}. Additionally, Test 34 began by flowing water in a straight stream at the ceiling in Room B for 30 seconds in a fixed position and then for 30 seconds in a clockwise application pattern. Then, the handline was aimed at Door AB, and again water was applied for 30 seconds in a fixed position and for 30 seconds in a clockwise pattern. These steps were repeated for narrow fog and wide fog streams. Additionally, the procedure was repeated for the three types of streams, except a counter clockwise pattern was applied.

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_33_34}
\caption[East Structure layout for Tests 33 and 34]{East Structure layout for Tests 33 and 34}
\label{fig:test_33_34_setup}
\end{figure}
\FloatBarrier
